Verifying Demonstrations

### 2020-07-03 paper/conclusions.tex
Adds scenario from conclusions to intro

In this paper, we have adapted the Schnorr protocol as a
distance-bounding protocol.  It allows to construct distance-bounding
general attribute-based authentication, more general attributes than
provided by previous \ac{DB} ones.  With our contribution, Alice can
now prove more complex statements to Bob; \eg that she is older than 18 
(without revealing her actual age), has a cinema subscription which is not 
\enquote{double spent} by someone else at the same time and, at the same time, 
Bob can be sure that Alice is not just relaying messages from her older sister 
Carol or \ac{DBMF} relaying the subscription from some unsuspecting stranger.

>>>>

In this paper, we have adapted the Schnorr protocol as a
distance-bounding protocol.  It allows to construct distance-bounding
general attribute-based authentication, more general attributes than
provided by previous \ac{DB} ones.  With our contribution, Alice can
now prove more complex statements to Bob; \eg that she is older than 18 
(without revealing her actual age), has a cinema subscription which is not 
\enquote{double spent} by someone else at the same time~\cite[\eg][]{AnonPass} 
and, at the same time, Bob can be sure that Alice is not just relaying messages 
from her older sister Carol or \ac{DBMF} relaying the subscription from some 
unsuspecting stranger also waiting in the queue to enter.

### 2020-07-03 paper/intro.tex
Moves formal verification completely to the appendix
Adds scenario from conclusions to intro

Our work present contributions in the area of \ac{DB} public-key protocols, 
particularly \ac{DB} \acp{ZKPK}.
This allows anyone to act as a verifier, unlike in the shared-key scenario 
where the verifier must be trusted.
The \ac{ZK} property also enables a variety of privacy properties, such as 
anonymity.

>>>>

Our work present contributions in the area of \ac{DB} public-key protocols, 
particularly \ac{DB} \acp{ZKPK}.
This allows anyone to act as a verifier, unlike in the shared-key scenario 
where the verifier must be trusted.
The \ac{ZK} property also enables a variety of privacy properties, such as 
anonymity.
With our contribution, Alice can
now prove more complex statements to Bob; \eg that she is older than 18 
(without revealing her actual age), has a cinema subscription which is not 
\enquote{double spent} by someone else at the same time~\cite[\eg][]{AnonPass} 
and, at the same time, Bob can be sure that Alice is not just relaying messages 
from her older sister Carol or \ac{DBMF} relaying the subscription from some 
unsuspecting stranger also waiting in the queue to enter.
